---
title: "Chapter 4 - R4DS"
author: "Brett Whitney"
date: "1/26/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chapter 4 - Workflow Basics

Welcome to my notes on chapter 4 of R for Data Science! You might notice that I switched to making these notes in a `.Rmd` document rather than a `.R` script. This is primarily due to the length and composition of my notes for chapter three; it seemed the balance of my notes were prose rather than code. 

Note that because I'm not brand new to R and RStudio, I am already familiar with a lot of the tips in this chapter so my notes are only going to highlight new stuff, quotes, etc that are meaningful to me. 

**The only way to get over [being frustrated] is to keep trying**

**Code is miserable to read on a good day** - so use good formatting practices.

### New Tricks
For the console - say I have an object with a cumbersome name like `this_is_a_really_long_name` and I recently (in the current session) assigned it a value of 2.5 using this code: 

```{r console_trick}
this_is_a_really_long_name <- 2.5
```

Now I want to assign it the value 3.5 instead. By typing enough of the object name (ie `this`) I can then use the shortcut ctrl + up to get a list of previously executed commands starting with that string of letters. I can use the arrow keys to select the command I want to edit, hit enter, then edit the command without retyping the whole thing. 

You can make assignment and printing the value of an object happen simultaneously by surrounding a statement with regular old parentheses.
```{r assign_and_print}
(y <- seq(1, 10, length.out = 5))
```

### Exercises
1. Why does this code not work?
```{r q1_code_prompt}
my_variable <- 10
my_varıable
```
Haha, this code is suppposed to produce an error saying `my_varıable` doesn't exist, but for some reason it's giving me the value of 10 assigned to `my_variable`. It should error out because they use two different characters for the letter 'i'. 

2. Tweak each of the following R commands so that they run correctly:

Original commands:
```{r q2_code_prompt, eval = FALSE}
ggplot(dota = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8)
filter(diamond, carat > 3)
```

Fixed commands:
```{r q2_code_response}
library(tidyverse)

ggplot(data = mpg) + # typo in "data" argument name
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8) # typo in filter() function call and misuse of "=" for comparison
filter(diamonds, carat > 3) # typo in data set name
```

3. Press Alt + Shift + K. What happens? How can you get to the same place using the menus?

Keyboard shortcuts, woot woot. Help -> Keyboard Shortcuts Help in the top level toolbar brings up the same shortcut cheatsheet. 